Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
updated data table

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Data & Features & Gesture Types & Accuracy \\ \hline
  No	&	Simple	&	Gyro	&	circle \& triangle	&	87.7\% \\ \hline
  No	&	Simple	&	Accel	&	circle \& triangle	&	87.7\% \\ \hline
  No	&	Simple	&	Accel and Gyro	&	circle \& triangle	&	96.7\% \\ \hline
  Yes	&	Simple	&	Accel and Gyro	&	circle \& triangle	&	90.7\% \\ \hline
  No	&	Complex	&	Accel and Gyro	&	circle \& triangle	&	89.5\% \\ \hline
  Yes	&	Complex	&	Accel and Gyro	&	circle \& triangle	&	91.9\% \\ \hline
  Yes	&	Complex	&	Accel	&	up-flip \& right-flip	&	91.0\% \\ \hline
  Yes	&	Complex	&	Gyro	&	up-flip \& right-flip	&	100\% \\ \hline
  Yes	&	Complex	&	Accel and Gyro	&	up-flip \& right-flip	&	100\% \\ \hline
  Yes	&	Complex	&	Accel	&	up-flip, right-flip, circle, triangle, and bowl	&	87.9\% \\ \hline
  Yes	&	Complex	&	Gyro	&	up-flip, right-flip, circle, triangle, and bowl	&	89.8\% \\ \hline
  Yes	&	Complex	&	Accel and Gyro	&	up-flip, right-flip, circle, triangle, and bowl	&	90.0\% \\
  \hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Features & Gestures Types & Accuracy \\ \hline
  Yes	&	Both  &	All &	94.6\% \\ \hline
  Yes	&	Both	&	All &	89.6\% \\ \hline
  Yes	&	Accel &	All &	92.0\% \\ \hline
  Yes	&	Accel &	All &	84.2\% \\ \hline
  Yes	&	Gyro  &	All &	92.3\% \\ \hline
  Yes	&	Gyro  &	All &	89.7\% \\ \hline
  Yes	&	Both	&	All &	96.7\% \\ \hline
  Yes	&	Both	&	All &	97.9\% \\ \hline
  Yes	&	Both  &	All &	98.4\% \\ \hline
  No	&	Both	&	All &	98.4\% \\ \hline
  Yes	&	Both	& Squares &	100\% \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Chance \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	72.0\% \\ \hline
  Yes	&	Both  & Circles and Reversed-circles  &	88.8\% \\
  \hline
\end{tabular}
\end{center}
